Quantifying and controlling biases in dark matter halo concentration estimates

### 2016-08-25 paper/ms.tex
agradecimientos

We then use an Affine Invariant Markov Chain Monte Carlo (MCMC)
implemented in the python module {\texttt{emcee}} \citep{emcee} to sample the
likelihood function distribution.
This runs roughly proportional to $N$. Using a single 2.3Ghz CPU core with two
walkers over 500 steps takes approximatly $0.5$ miliseconds per halo per
particle in the halo, i.e. a halo with $N=2\times 10^{3}$ can be fit
in one second approximately.

From the $\chi^2$ distribution we find the optimal value of the
concentration and its associated uncertainty. 
We stress that different choices for $\sigma^2_{\rm eff}$ do not
affect the optimal concentration value, only its uncertainty.

@@

These results show that using the integrated mass profile to estimate the
DM halo concentrations is a tool deserving deeper scrutiny.   
Further tests with larger simulated volumes, varying numerical
resolution, stacked data and different density profiles are the next
natural step to explore the full potential of this new method.

@@

 We acknowledge technical and financial support from Uniandes
 and Universidad de Antioquia.
 We acknowledge discussions with Tom\'as Verdugo, Stefan Gottloeber and Nelson
 Padilla.
 We thank the anonymous referee for comments that helped us improve
 the presentation of these results.

>>>>

We then use an Affine Invariant Markov Chain Monte Carlo (MCMC)
implemented in the python module {\texttt{emcee}} \citep{emcee} to sample the
likelihood function distribution.
From the $\chi^2$ distribution we find the optimal concentration value
and its associated uncertainty.   
We stress that different choices for $\sigma^2_{\rm eff}$ do not
affect the optimal concentration value, only its uncertainty.

Runtime is roughly proportional to $N$. Using a single 2.3Ghz CPU core with two
walkers over 500 steps takes $\sim 0.5$ miliseconds per halo per
particle in the halo, i.e. a halo with $N=2\times 10^{3}$ can be fit
in one second.

@@

These results show that using the integrated mass profile to estimate the
DM halo concentrations is a tool deserving deeper scrutiny.   
Further tests with larger simulated volumes, varying numerical
resolution, higher redshifts, stacked data and different density
profiles are the next natural step to explore the full potential of
this new method.

@@

 We acknowledge financial support from Uniandes
 and Universidad de Antioquia. 
 We thank Tom\'as Verdugo, Stefan Gottloeber and Nelson  Padilla for
their feedback.
We thank the anonymous referee for comments that improved
the presentation of these results.
